Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-31 analysis/paper/paper.qmd
Trimed gis map

ggplot() +
  geom_sf(data = veg_all, aes(fill = veg_all$ecoregion)) + #add color for vegetation polygons
  geom_sf(data = pts_all, aes(color = pts_all$min_tcsa)) +
  theme_minimal()

>>>>

ggplot() +
  geom_sf(data = veg_all, aes(fill = ecoregion)) + #add color for vegetation polygons
  geom_sf(data = pts_all, aes(color = min_tcsa)) +
  theme_minimal() +
  scale_fill_brewer(palette="Greys") +
  labs(fill="Ecoregion", color="TCSA")
